### 2015-08-26 LaTeX/coverLetter/rr_coverLetter.tex
added cover letter for resubmission

This letter accompanies our submission of a manuscript for your consideration. The manuscript ``Enemy at the Gates: Variation in Economic Growth from Civil Conflict'' applies a subnational spatial analysis to explain variation in macroeconomic performance amongst countries experiencing intrastate conflict. Our theoretical argument, bridges the economic development literature on the importance of cities with extant literature on the effect of armed conflict to provide a novel explanation for the paradox of high macroeconomic growth in conflict ridden countries. We think this is a very timely topic and an important contribution to an ongoing debate about the economic effects of instrastate conflict.\\[1ex]

@@

\includegraphics [scale=.8]{/Users/janus829/Dropbox/Finances/signature.png}

>>>>

This letter accompanies our resubmission of the manuscript ``Enemy at the Gates: Variation in Economic Growth from Civil Conflict'' (Manuscript ID: JCR- 14-0358), which applies a subnational spatial analysis to explain variation in macroeconomic performance amongst countries experiencing intrastate conflict. We feel confident that the revisions have made this a stronger manuscript and continue to think that the topic addressed by this manuscript is timely and serves an important contribution to the ongoing debate about the economic effects of instrastate conflict.\\[1ex]

@@

\includegraphics [scale=.8]{/Users/s7m/Dropbox/Finances/signature.png}
